Differential invariant signatures for planar Lie group transformations of images

### 2020-11-17 paper/newpaper.tex
conformal and mobius signatures updated

\documentclass[review,onefignum,onetabnum]{siamonline190516}
\usepackage{amsmath,amsfonts,graphicx}
\def\R{\mathbb{R}}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{tikz}
\usepackage{array}
\usepackage{natbib}

@@

An element of the special Euclidean group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as:
\begin{equation*}
  \begin{aligned}
    \bar{x} &= x\cos\theta  - y\sin\theta + t_x \\
    \bar{y} &= x\sin\theta  + y\cos\theta + t_y.
  \end{aligned}
\end{equation*}
We prolong the group action to form the jet space $J^2$ with coordinates $(x,
y, f, f_x, f_y, f_{xx}, f_{xy}, f_{yy})$ via the chain rule. The
transformation rule for the derivatives is given by:
\begin{equation}
  \begin{bmatrix}
  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar{x}\bar{x}} \\ \bar f_{\bar{x}\bar{y}} \\ \bar f_{\bar{y}\bar{y}}
  \end{bmatrix} = 
  \begin{bmatrix}
 c & -s & 0 & 0 & 0 \\
 s & c & 0 & 0 & 0 \\
0 & 0 & c^2 & -2cs & s^2 \\
0 & 0 & cs & c^2 - s^2 & -cs \\
0 & 0 & s^2 & 2cs & c^2 \\
  \end{bmatrix}
  \begin{bmatrix}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
  \end{bmatrix},
\label{eqn:SE2}
 \end{equation}
where $c = \cos \theta$ and $s = \sin \theta$. Because the group has three
parameters, we choose the cross section of the group orbits to be $\bar{x}
= 0, \bar{y} = 0, \bar{f}_{\bar{y}} = 0$. We also require that $\bar{f}_{x}
> 0$ to uniquely define the moving frame. Note that the group action is
locally free (away from critical points) when prolonged to $J^1$, however
we prolonged to $J^2$ in order to compute invariants. points. The moving
frame is then given by the prolonged Euclidean transformation that maps an
element of  $J^2$ to this cross section. It can be thought of as rotating
the image about that point so that its gradient is pointing in the positive
$x$ direction, and then translating the image so the point is mapped to the
origin.

@@

The remaining elements not fixed by the cross section, $\bar{f}$,
$\bar{f}_{\bar{x}}$, $\bar{f}_{\bar{x}\bar{x}}$,
$\bar{f}_{\bar{x}\bar{y}}$, and $\bar{f}_{\bar{y}\bar{y}}$ are therefore
all invariant. This gives the following set of invariants:
\begin{equation}\label{eq:se2invariants}
\begin{aligned}
  I_0 &= f \\
  I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= I_1\bar{f}_{\bar{x}\bar{x}}) \\
  I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= I_1\bar{f}_{\bar{x}\bar{y}})\\
  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}}).
\end{aligned}
\end{equation}
Note that we multiplied each of the second derivative invariants by $I_1$
so that they would decay smoothly to zero at critical points.

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
\caption{A sample $SE(2)$ Transform and 3D signature.}
\label{fig:SE2}
\end{figure}
\subsection{The Euclidean Group E(2)}
An element of the Euclidean group $E(2)$ maps an element $(x, y)$ of
$\mathbb{R}^2$ to $(\bar{x}, \bar{y})$ as:
\begin{equation*}
  \begin{aligned}
    \bar{x} &=  x\varepsilon\cos\theta  - y\varepsilon\sin\theta + t_x \\
    \bar{y} &= x\sin\theta  + y\cos\theta + t_y.
  \end{aligned}
\end{equation*}
where $\varepsilon \in \{-1, 1\}$ and the remaining parameters are the same
as for $SE(2)$. If $\varepsilon = 1$ it is a rigid transformation, and if
$\varepsilon = -1$ it contains a reflection.

@@

We begin by choosing the same cross section as for $SE(2)$, namely $\bar{x} = 0,
\bar{y} = 0, \bar{f}_{\bar{y}} = 0, \bar{f}_{\bar{x}} > 0$. This gives
$\cos\theta = \varepsilon f_x / \lVert \nabla f \rVert$ and $\sin\theta =
-\varepsilon f_y / \lVert \nabla f \rVert$. Under this transformation,
regardless of whether $\varepsilon = 1$ or $\varepsilon = -1$, the
derivative $\bar{f}_{\bar{x}} = \lVert \nabla f \rVert$. We need a second
derivative term to resolve the choice of $\varepsilon$ for the moving
frame. The only second derivative term in which $\varepsilon$ appears is
the $\bar{f}_{\bar{x}\bar{y}}$ term. Substituting in for $\cos\theta,
\sin\theta$, we see that:
\begin{equation*}
    \bar{f}_{\bar{x}\bar{y}} = \frac{\varepsilon(f_xf_y(f_{yy} - f_{xx}) + (f_x^2 -
    f_y^2)f_{xy})}{f_x^2 + f_y^2}.
\end{equation*}
This suggests choosing $\varepsilon$ to make $\bar{f}_{\bar{x}\bar{y}} \ge
0$. We can then list the invariants:
\begin{equation}\label{eq:e2invariants}
\begin{aligned}
  I_0 &= f \\
  I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= I_1\bar{f}_{\bar{x}\bar{x}}) \\
  I_3 &= \lvert f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2)\rvert
  &&(= I_1\lvert \bar{f}_{\bar{x}\bar{y}}\rvert)\\
  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}}).
\end{aligned}
\end{equation}
Notice that most, but not all of the $SE(2)$ invariants
\eqref{eq:se2invariants} are also $E(2)$ invariants. We again multiply
through the invariants by $I_1$ so that they decay smoothly at critical
points.

These invariants are a functionally independent, complete, set of polynomial differential invariants up to second derivatives. Note that the invariants found previously by tensor contraction Eq. (\ref{eq:se2}) in Section~\ref{sec:contraction} can be expressed in terms of these:
\begin{align*}
  f = f &= I_0 \\
  f_if_i = f_x^2 + f_y^2 &= I_1 \\
  f_{ii} = f_{xx} + f_{yy} &= \frac{I_2 + I_4}{I_1} \\
  f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 &= \frac{I_2^2 + I_4^2 + 2I_3^2}{I_1^2} \\
  f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy} &= I_2.
\end{align*}

@@

The four third-order invariants can be deduced from the moving frame. They are rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.  Clearing denominators so as to work with polynomials, we choose $M_1 = (f_{xx} + f_{yy})^4$ and two of the four third-order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where: 
\begin{align} M_2&=
f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
 f_y ^3 f_{yyy} f_x ^2 + \frac{3}{2} f_{yy}^2 f_x ^4 - 
 9 f_y ^3 f_{yy} f_x  f_{xy} + 
 3 f_y  f_{yy} f_x ^3 f_{xy} + \frac{3}{2} f_y ^4 f_{xy}^2 \\ \nonumber
 &- 9 f_y ^2 f_x ^2 f_{xy}^2 
+ \frac{3}{2} f_z ^4 f_{xy}^2 + 
 3 f_y ^4 f_x  f_{xyy} + 3 f_y ^2 f_x ^3 f_{xyy} + 
 3 f_y ^4 f_{yy} f_{xx} + 3 f_{yy} f_x ^4 f_{xx} + 
 3 f_y ^3 f_x  f_{xy} f_{xx} \\ \nonumber
&- 9 f_y  f_x ^3 f_{xy} f_{xx} 
+ \frac{3}{2} f_y ^4 f_{xx}^2 + 
 \frac{9}{2} f_y ^2 f_x ^2 f_{xx}^2 + 3 f_y ^3 f_x ^2 f_{xxy} + 
 3 f_y  f_x ^4 f_{xxy} + f_y ^2 f_x ^3 f_{xxx} + 
 f_x ^5 f_{xxx}, 
\end{align}

\begin{align}
M_3&=-3 f_y  f_{yy}^2 f_x ^3 + 
 f_y ^2 f_{yyy} f_x ^3 + f_{yyy} f_x ^5 + 
 9 f_y ^2 f_{yy} f_x ^2 f_{xy} - 
 3 f_{yy} f_x ^4 f_{xy} - 6 f_y ^3 f_x  f_{xy}^2 + 
 6 f_y  f_x ^3 f_{xy}^2 \\ \nonumber
&- 3 f_y ^3 f_x ^2 f_{xyy} - 
 3 f_y  f_x ^4 f_{xyy} - 3 f_y ^3 f_{yy} f_x  f_{xx} + 
 3 f_y  f_{yy} f_x ^3 f_{xx} + 3 f_y ^4 f_{xy} f_{xx} - 
 9 f_y ^2 f_x ^2 f_{xy} f_{xx} \\ \nonumber
 &+ 3 f_y ^3 f_x  f_{xx}^2 + 3 f_y ^4 f_x  f_{xxy} + 
 3 f_y ^2 f_x ^3 f_{xxy} - f_y ^5 f_{xxx} - 
 f_y ^3 f_x ^2 f_{xxx}.
\end{align}

The image $f$ and these 3 relative invariants of weight 8 provide a three-dimensional signature; an example is shown in Figure~\ref{fig:mobius}, although note that it is singular when $f_x=f_y=f_{xx}+f_{yy}=0$, a codimension 1 phenomenon for images.

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_Mobius.png}
\includegraphics[width=.45\textwidth]{Figs/Mobius_signature.png}
\caption{A sample M\"obius Transform and 3D signature.}
\label{fig:mobius}
\end{figure}

@@

It is convenient to work in the complex variable $z = x + iy$. Without loss of
generality, we can assume $x = y = 0$. We begin the construction of our
cross section by choosing $\bar{x} = \bar{y} = 0$. Then, $\psi^{-1}$ 
can be represented locally by a Taylor series of the form:
\begin{equation*}
    z = \psi^{-1}(\bar{z}) = c_1 \bar{z} + c_2 \bar{z}^2 + c_3\bar{z}^3 + \cdots,
\end{equation*}
where $c_k = a_k + ib_k, k = 1, 2, \ldots$. We solve for the parameters
$a_k, b_k$ in stages.  To find $c_1 = a_1 + i b_1$ we need two constraints.
Differentiating $f(x, y) = \bar{f}(\bar{x}, \bar{y})$ and substituting in
our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives:
\begin{align*}
    \bar{f}_{\bar{x}} = f_x x_{\bar{x}} + f_y y_{\bar{x}} &= a_1 f_x + b_1
    f_y, \\
    \bar{f}_{\bar{y}} = f_x x_{\bar{y}} + f_y y_{\bar{y}} &= -b_1 f_x + a_1
    f_y. 
\end{align*}
Note that $\bar{x} = \bar{y} = 0$ removes all higher order derivatives from
the cross section equation. Adding two extra constraints to the cross
section, $\bar{f}_{\bar{x}} = 1, \bar{f}_{\bar{y}} = 0$, this system is readily
solved to give :
\begin{equation*}
    \begin{aligned}
        a_1 &= f_x / (f_x^2 + f_y^2), &  b_1 &= f_y / (f_x^2 + f_y^2).
    \end{aligned}
\end{equation*}
We then repeat the process, this time using the second derivative
computations. This time, there are two new parameters, $a_2, b_2$, to solve
for, but there are three derivatives. We use the cross section equations
$\bar{f}_{\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{y}} = 0$ to solve for
$a_2$ and $b_2$, the remaining derivative $\bar{f}_{\bar{y}\bar{y}}$ is then the
sole second-order invariant, which we also saw for the M\"obius group: 
\begin{equation}
    \bar{f}_{\bar{y}\bar{y}} = \frac{f_{xx} + f_{yy}}{f_x^2 + f_y^2}.
\label{eqn:C1}
\end{equation}
Continuing in this way, at derivative order $n$ two real group parameters
enter: $a_n$ and $b_n$. There are $n+1$ independent derivatives of $f$ of
order $n$, so there must be $n-1$ new independent invariants at each order.
Hence at third order there are two more invariants, using the constraints
$\bar{f}_{\bar{x}\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{x}\bar{y}} = 0$,
the remaining derivatives are invariant:
\begin{align}
    \bar{f}_{\bar{x}\bar{y}\bar{y}} &= \frac{1}{(f_x^2 + f_y^2)^3} \left[
f_y^3f_{yyy} + f_x^2f_yf_{yyy}
            -2f_y^2f_{yy}^2 - 2f_{xx}f_y^2f_{yy} -
            4f_xf_{xy}f_yf_{yy} - 2f_x^2 f_{xx}f_{yy} \right. \\ \nonumber
&+ \left. f_{xxy}f_y^3 +
            f_x^2 f_{xxy}f_y - 4 f_x f_{xy} f_{xx} f_y + f_x^3 f_{xxx} -
        2f_x^2 f_{xx}^2 + f_x^3 f_{xyy} \right] 
\\ \label{eqn:C2}
        \bar{f}_{\bar{y}\bar{y}\bar{y}} &= \frac{1}{(f_x^2 + f_y^2)^3} \left[
f_xf_y^2f_{yyy} +
        f_x^3f_{yyy} - 2f_x f_y f_{yy}^2 + 2f_{xy}f_y^2f_{yy} -
    2f_x^2f_{xy}f_{yy} - f_{xxx}f_y^3 \right. \\ \nonumber
&- \left. f_{xyy}f_y^3 + f_xf_{xxy}f_y^2 +
2f_{xy}f_{xx}f_y^2 - f_x^2 f_{xxx} f_y + 2f_xf_{xx}^2 f_y - f_x^2 f_{xyy}
f_y + f_x^3 f_{xxy} - 2f_x^2 f_{xy} f_{xx} \right] \label{eqn:C3}
\end{align}

Note that the denominators of all three of these equations are the same up to index. We therefore clear denominators as usual and form the three-dimensional signature ((\ref{eqn:C1})$^3$,(\ref{eqn:C2}),(\ref{eqn:C3})). We then project them into the unit sphere and multiply by $f$ to constrain them. This signature is continuous at all $(x,y)$ such that the three quantities are not simultaneously equal to zero, which occurs when $f_x = f_y = f_{xx} = f_{yy} = 0$, which is a codimension-1 phenomenon for images.

>>>>

\documentclass[review,onefignum,onetabnum]{siamonline190516}
\usepackage{amsmath,amsfonts,graphicx}
\def\R{\mathbb{R}}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{tikz}
\usepackage{array}
\usepackage{natbib}

@@

An element of the special Euclidean group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as:
\begin{equation*}
  \begin{aligned}
    \bar{x} &= x\cos\theta  - y\sin\theta + t_x \\
    \bar{y} &= x\sin\theta  + y\cos\theta + t_y.
  \end{aligned}
\end{equation*}
We prolong the group action to form the jet space $J^2$ with coordinates $(x,
y, f, f_x, f_y, f_{xx}, f_{xy}, f_{yy})$ via the chain rule. The
transformation rule for the derivatives is given by:
\begin{equation}
  \begin{bmatrix}
  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar{x}\bar{x}} \\ \bar f_{\bar{x}\bar{y}} \\ \bar f_{\bar{y}\bar{y}}
  \end{bmatrix} = 
  \begin{bmatrix}
 c & -s & 0 & 0 & 0 \\
 s & c & 0 & 0 & 0 \\
0 & 0 & c^2 & -2cs & s^2 \\
0 & 0 & cs & c^2 - s^2 & -cs \\
0 & 0 & s^2 & 2cs & c^2 \\
  \end{bmatrix}
  \begin{bmatrix}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
  \end{bmatrix},
\label{eqn:SE2}
 \end{equation}
where $c = \cos \theta$ and $s = \sin \theta$. Because the group has three
parameters, we choose the cross section of the group orbits to be $\bar{x}
= 0, \bar{y} = 0, \bar{f}_{\bar{y}} = 0$. We also require that $\bar{f}_{x}
> 0$ to uniquely define the moving frame. Note that the group action is
locally free (away from critical points) when prolonged to $J^1$, however
we prolonged to $J^2$ in order to compute invariants. The moving
frame is then given by the prolonged Euclidean transformation that maps an
element of  $J^2$ to this cross section. It can be thought of as rotating
the image about that point so that its gradient is pointing in the positive
$x$ direction, and then translating the image so the point is mapped to the
origin.

@@

The remaining elements not fixed by the cross section, $\bar{f}$,
$\bar{f}_{\bar{x}}$, $\bar{f}_{\bar{x}\bar{x}}$,
$\bar{f}_{\bar{x}\bar{y}}$, and $\bar{f}_{\bar{y}\bar{y}}$ are therefore
all invariant. This gives the following set of invariants:
\begin{equation}\label{eq:se2invariants}
\begin{aligned}
  K_0 &= f \\
  K_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
  K_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= K_1\bar{f}_{\bar{x}\bar{x}}) \\
  K_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= K_1\bar{f}_{\bar{x}\bar{y}})\\
  K_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= K_1\bar{f}_{\bar{y}\bar{y}}).
\end{aligned}
\end{equation}
Note that we multiplied each of the second derivative invariants by the
invariant $K_1$ so that they would decay smoothly to zero at critical
points.  Interestingly, $K_4$ is the affine invariant $D$ from
\eqref{eq:cde} and $K_1, K_2$ are also Euclidean invariants, so we need to
include $K_3$ in our signature. We choose our signature to be
\begin{equation}
    \label{eq:SE2signature}
    I_{SE(2)}(f) = (f, K_1, K_3)
\end{equation}
Fig.~\ref{fig:SE2} shows the signature of our test image under a sample
transformation of $SE(2)$:
\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
\caption{A sample $SE(2)$ Transform and 3D signature.}
\label{fig:SE2}
\end{figure}

\subsection{The Euclidean Group E(2)}
An element of the Euclidean group $E(2)$ maps an element $(x, y)$ of
$\mathbb{R}^2$ to $(\bar{x}, \bar{y})$ as:
\begin{equation*}
  \begin{aligned}
    \bar{x} &=  x\varepsilon\cos\theta  - y\varepsilon\sin\theta + t_x \\
    \bar{y} &= x\sin\theta  + y\cos\theta + t_y.
  \end{aligned}
\end{equation*}
where $\varepsilon \in \{-1, 1\}$ and the remaining parameters are the same
as for $SE(2)$. If $\varepsilon = 1$ it is a rigid transformation, and if
$\varepsilon = -1$ it contains a reflection.

@@

We begin by choosing the same cross section as for $SE(2)$, namely $\bar{x} = 0,
\bar{y} = 0, \bar{f}_{\bar{y}} = 0, \bar{f}_{\bar{x}} > 0$. This gives
$\cos\theta = \varepsilon f_x / \lVert \nabla f \rVert$ and $\sin\theta =
-\varepsilon f_y / \lVert \nabla f \rVert$. Under this transformation,
regardless of whether $\varepsilon = 1$ or $\varepsilon = -1$, the
derivative $\bar{f}_{\bar{x}} = \lVert \nabla f \rVert$. We need a second
derivative term to resolve the choice of $\varepsilon$ for the moving
frame. The only second derivative term in which $\varepsilon$ appears is
the $\bar{f}_{\bar{x}\bar{y}}$ term. Substituting in for $\cos\theta,
\sin\theta$, we see that:
\begin{equation*}
    \bar{f}_{\bar{x}\bar{y}} = \frac{\varepsilon(f_xf_y(f_{yy} - f_{xx}) + (f_x^2 -
    f_y^2)f_{xy})}{f_x^2 + f_y^2}.
\end{equation*}
This suggests choosing $\varepsilon$ to make $\bar{f}_{\bar{x}\bar{y}} \ge
0$. The moving frame is then fully specified, and the remaining derivatives
give the same invariants $K_0, K_1, K_2, K_4$ as for $SE(2)$,
\eqref{eq:se2invariants}, the one difference being $\hat{K}_3$:
\begin{equation}\label{eq:e2invariants}
    \hat{K}_3 = \lvert f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2)\rvert
\end{equation}

These invariants are a functionally independent, complete, set of
polynomial differential invariants up to second derivatives. Note that the
invariants found previously by tensor contraction Eq. (\ref{eq:e2tensor}) in
Section~\ref{sec:contraction} can be expressed in terms of these:
\begin{align*}
  f = f &= K_0 \\
  f_if_i = f_x^2 + f_y^2 &= K_1 \\
  f_{ii} = f_{xx} + f_{yy} &= \frac{K_2 + K_4}{K_1} \\
  f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 &= \frac{K_2^2 + K_4^2 + 2K_3^2}{K_1^2} \\
  f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy} &= K_2.
\end{align*}

@@

The four third-order invariants can be deduced from the moving frame. They
are rational functions with numerators of degree 6 and denominators $(f_x^2
+ f_y^2)^4$, and are relative invariants of weight 8.  Clearing
denominators so as to work with polynomials, we choose $M_1 = (f_{xx} +
f_{yy})^4$ and two of the four third-order invariants $M_2$ and $M_3$:
\begin{align*} M_2&=
f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
 f_y ^3 f_{yyy} f_x ^2 + \frac{3}{2} f_{yy}^2 f_x ^4 - 
 9 f_y ^3 f_{yy} f_x  f_{xy} + 
 3 f_y  f_{yy} f_x ^3 f_{xy} + \frac{3}{2} f_y ^4 f_{xy}^2 \\ \nonumber
 &- 9 f_y ^2 f_x ^2 f_{xy}^2 
+ \frac{3}{2} f_z ^4 f_{xy}^2 + 
 3 f_y ^4 f_x  f_{xyy} + 3 f_y ^2 f_x ^3 f_{xyy} + 
 3 f_y ^4 f_{yy} f_{xx} + 3 f_{yy} f_x ^4 f_{xx} + 
 3 f_y ^3 f_x  f_{xy} f_{xx} \\ \nonumber
&- 9 f_y  f_x ^3 f_{xy} f_{xx} 
+ \frac{3}{2} f_y ^4 f_{xx}^2 + 
 \frac{9}{2} f_y ^2 f_x ^2 f_{xx}^2 + 3 f_y ^3 f_x ^2 f_{xxy} + 
 3 f_y  f_x ^4 f_{xxy} + f_y ^2 f_x ^3 f_{xxx} + 
 f_x ^5 f_{xxx}, 
\end{align*}

\begin{align*}
M_3&=-3 f_y  f_{yy}^2 f_x ^3 + 
 f_y ^2 f_{yyy} f_x ^3 + f_{yyy} f_x ^5 + 
 9 f_y ^2 f_{yy} f_x ^2 f_{xy} - 
 3 f_{yy} f_x ^4 f_{xy} - 6 f_y ^3 f_x  f_{xy}^2 + 
 6 f_y  f_x ^3 f_{xy}^2 \\ \nonumber
&- 3 f_y ^3 f_x ^2 f_{xyy} - 
 3 f_y  f_x ^4 f_{xyy} - 3 f_y ^3 f_{yy} f_x  f_{xx} + 
 3 f_y  f_{yy} f_x ^3 f_{xx} + 3 f_y ^4 f_{xy} f_{xx} - 
 9 f_y ^2 f_x ^2 f_{xy} f_{xx} \\ \nonumber
 &+ 3 f_y ^3 f_x  f_{xx}^2 + 3 f_y ^4 f_x  f_{xxy} + 
 3 f_y ^2 f_x ^3 f_{xxy} - f_y ^5 f_{xxx} - 
 f_y ^3 f_x ^2 f_{xxx}.
\end{align*}
We then form a signature by our usual projection method from the image $f$
and these three weight $8$ relative invariants:
\begin{equation}
    \label{eq:mobiussignature}
    \mathcal{I}_{\text{M\"obius}}(f) = \frac{f}{\sqrt{M_1^2 + M_2^2 +
    M_3^2}} (M_1, M_2, M_3)
\end{equation}
An example is shown in Figure~\ref{fig:mobius}, although note that the
signature is singular when $f_x=f_y=f_{xx}+f_{yy}=0$, a codimension 1
phenomenon for images. 
\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_Mobius.png}
\includegraphics[width=.45\textwidth]{Figs/Mobius_signature.png}
\caption{A sample M\"obius Transform and 3D signature.}
\label{fig:mobius}
\end{figure}

@@

@@

It is convenient to work in the complex variable $z = x + iy$. Without loss of
generality, we can assume $x = y = 0$. We begin the construction of our
cross section by choosing $\bar{x} = \bar{y} = 0$. Then, $\psi^{-1}$ 
can be represented locally by a Taylor series of the form:
\begin{equation*}
    z = \psi^{-1}(\bar{z}) = c_1 \bar{z} + c_2 \bar{z}^2 + c_3\bar{z}^3 + \cdots,
\end{equation*}
where $c_k = a_k + ib_k, k = 1, 2, \ldots$. We solve for the parameters
$a_k, b_k$ in stages.  To find $c_1 = a_1 + i b_1$ we need two constraints.
Differentiating $f(x, y) = \bar{f}(\bar{x}, \bar{y})$ and substituting in
our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives:
\begin{align*}
    \bar{f}_{\bar{x}} = f_x x_{\bar{x}} + f_y y_{\bar{x}} &= a_1 f_x + b_1
    f_y, \\
    \bar{f}_{\bar{y}} = f_x x_{\bar{y}} + f_y y_{\bar{y}} &= -b_1 f_x + a_1
    f_y. 
\end{align*}
Note that $\bar{x} = \bar{y} = 0$ removes all higher order derivatives from
the cross section equation. Adding two extra constraints to the cross
section, $\bar{f}_{\bar{x}} = 1, \bar{f}_{\bar{y}} = 0$, this system is readily
solved to give :
\begin{equation*}
    \begin{aligned}
        a_1 &= f_x / (f_x^2 + f_y^2), &  b_1 &= f_y / (f_x^2 + f_y^2).
    \end{aligned}
\end{equation*}
We then repeat the process, this time using the second derivative
computations. This time, there are two new parameters, $a_2, b_2$, to solve
for, but there are three derivatives. We use the cross section equations
$\bar{f}_{\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{y}} = 0$ to solve for
$a_2$ and $b_2$, the remaining derivative $\bar{f}_{\bar{y}\bar{y}}$ is then the
sole second-order invariant, which we also saw for the M\"obius group: 
\begin{equation}
    \bar{f}_{\bar{y}\bar{y}} = \frac{f_{xx} + f_{yy}}{f_x^2 + f_y^2} =
    \frac{C_1}{f_x^2 + f_y^2}.
\label{eqn:C1}
\end{equation}
Continuing in this way, at derivative order $n$ two real group parameters
enter: $a_n$ and $b_n$. There are $n+1$ independent derivatives of $f$ of
order $n$, so there must be $n-1$ new independent invariants at each order.
Hence at third order there are two more invariants, using the constraints
$\bar{f}_{\bar{x}\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{x}\bar{y}} = 0$,
the remaining derivatives are invariant:
\begin{align}
    \bar{f}_{\bar{x}\bar{y}\bar{y}} &= 
    \begin{multlined}[t]
        \frac{1}{(f_x^2 + f_y^2)^3} \left[
f_y^3f_{yyy} + f_x^2f_yf_{yyy}
            -2f_y^2f_{yy}^2 - 2f_{xx}f_y^2f_{yy} -
            4f_xf_{xy}f_yf_{yy} - 2f_x^2 f_{xx}f_{yy} \right. \\ 
+ \left. f_{xxy}f_y^3 +
            f_x^2 f_{xxy}f_y - 4 f_x f_{xy} f_{xx} f_y + f_x^3 f_{xxx} -
    2f_x^2 f_{xx}^2 + f_x^3 f_{xyy} \right]
    = \frac{C_2}{(f_x^2 +
f_y^2)^3}\end{multlined} \\
    \bar{f}_{\bar{y}\bar{y}\bar{y}} &= 
    \begin{multlined}[t]
        \frac{1}{(f_x^2 + f_y^2)^3} \left[
f_xf_y^2f_{yyy} +
        f_x^3f_{yyy} - 2f_x f_y f_{yy}^2 + 2f_{xy}f_y^2f_{yy} -
    2f_x^2f_{xy}f_{yy} - f_{xxx}f_y^3 \right. \\ 
-  f_{xyy}f_y^3 + f_xf_{xxy}f_y^2 +
2f_{xy}f_{xx}f_y^2 - f_x^2 f_{xxx} f_y + 2f_xf_{xx}^2 f_y - f_x^2 f_{xyy}
f_y \\\left.+ f_x^3 f_{xxy} - 2f_x^2 f_{xy} f_{xx}\right]
= \frac{C_3}{(f_x^2 + f_y^2)^3}
\end{multlined}\label{eqn:C3}
\end{align}
Note that the denominators of all three of these equations are the same up
to index. We therefore clear denominators as usual and form the
signature using our usual projection technique:
\begin{equation}
    \label{eq:conformalsignature}
\mathcal{I}_{\text{Diff}_\text{con}}(f) = \frac{f}{\sqrt{C_1^6 + C_2^2 +
C_3^2}}(C_1^3, C_2, C_3)
\end{equation}
This signature is continuous at all $(x,y)$ such that the three quantities
are not simultaneously equal to zero, which occurs when $f_x = f_y = f_{xx}
= f_{yy} = 0$, which is a codimension-1 phenomenon for images.

An example for the conformal map $\varphi$ defined through $\varphi^{-1}$ by
$\varphi^{-1}(z) = \frac{3}{8}(z - 2)^2 - \frac{3}{2}$ is shown in
Figure~\ref{fig:Diffcon}.
\begin{figure}
\centering 
\includegraphics[width=.45\textwidth]{Figs/f_transformed_Diffcon.png}
\includegraphics[width=.45\textwidth]{Figs/Diffcon_signature.png}
\caption{A sample $\text{Diff}_{con}$ Transform and 3D signature.}
\label{fig:Diffcon}
\end{figure}
